Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Added graphs for gravitational accuracy by run and hyperparameters

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}

@@

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{svg}

@@

This was not the only configuration that performed well; as seen in Figure \ref{grav_acc_by_run}, 10\% of the runs during the grid search produced accuracy greater than 93\%.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{grav_acc_by_run}
    \caption{\label{grav_acc_by_run} Accuracy of gravitational differentiation arranged by training run during the grid search.}
\end{figure}

As seen in Figure \ref{grav_acc_by_hyper}, all 3 hyperparameters that were optimized during the grid search had a significant effect on accuracy:
\begin{itemize}
    \item Smaller gravitational multipliers improved performance; the best value tested was 0.0005. This implies that the gravity effect on each unlabeled event should be weighted lightly compared to the labeled examples.
    \item Higher learning rates improve performance, with the best value tested at a quite high 0.03.
    \item Larger distortion powers (which raise the confidence threshold for a significant gravitational effect) improved performance, with the best tested at 11.
\end{itemize}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{grav_acc_by_hyper}
    \caption{\label{grav_acc_by_hyper} Accuracy of gravitational differentiation as a function of hyperparameter values.}
\end{figure}
